---
editor_options: 
  markdown: 
    wrap: 72
---

1.  **Install and Load Required Libraries**: First, install and load the
    necessary libraries.

```{r}
# Install the required packages
install.packages("datasets")
install.packages("caret")
install.packages("ggplot2")
	
# Load the libraries
library(datasets)
library(caret)
library(ggplot2)
```

```{r}
getwd()
```

2.  **Load the MyIris Dataset**: Load the MyIris dataset which is
    available in the `datasets` package.

```{r}
# Load the MyIris dataset
setwd("C:/Users/hp/Documents/CODSOFT")
MyIris<-read.csv("IRIS.csv")
MyIris
View(MyMyIris)
```

3.  **Exploratory Data Analysis (EDA)**: Perform some exploratory data
    analysis to understand the dataset better.

```{r}
# Summary of the dataset
summary(MyIris)

# Plot the data
ggplot(MyIris, aes(x = sepal_length, y = sepal_width, color = species)) +
  geom_point() +
  labs(title = "sepal_length vs sepal_width")

ggplot(MyIris, aes(x = petal_length, y = petal_width, color = species)) +
  geom_point() +
  labs(title = "petal_length vs petal_width")
```

4.  **Split the Data into Training and Testing Sets**: Split the dataset
    into training and testing sets.

```{r}
# Set seed for reproducibility
set.seed(123)

# Split the data
trainIndex <- createDataPartition(MyIris$species, p = 0.7, list = FALSE)
trainData <- MyIris[trainIndex,]
testData <- MyIris[-trainIndex,]
```

5.  **Train a Model**: Train a machine learning model. We'll use the
    k-Nearest Neighbors (k-NN) algorithm for this example.

```{r}
# Train the model using k-NN
model <- train(species ~ ., data = trainData, method = "knn", tuneLength = 10)
print(model)
```

6.  **Evaluate the Model**: Evaluate the performance of the model using
    the testing set.

```{r}
# Make predictions on the test set
predictions <- predict(model, newdata = testData)

# Confusion matrix
confusionMatrix(predictions, testData$species)
```
